A Proposal for the Use of Backtranslation to Decode Whale Songs

### 2024-07-01 tex/paper.tex
fixed weird wording

\section{Putting it all together}
The penalties are used for reinforcement learning applied to $M_{we}$. This process is repeated for all available paragraphs, potentially tens of thousands of times, effectively fine-tuning the model on a paragraph-by-paragraph basis.
Here is a summary of the training algorithm above:
\begin{algorithm}
\caption{Backtranslation Algorithm}
\begin{algorithmic}[1]
\STATE Initialize parameters $\theta$
\FOR{each iteration}
\STATE Translate whale vocalizations to English
\STATE Calculate probability penalty $Pwe$
\STATE Translate English back to whale
\STATE Calculate contextual and semantic penalties $Pwew$ and $Psd$
\STATE Update parameters $\theta$ based on combined penalties
\ENDFOR
\end{algorithmic}
\end{algorithm}
\subsection{Datasets}
The datasets provided a comprehensive set of whale vocalizations and environmental contexts, essential for training and evaluating our models.
We analyze the results of three datasets:

@@

2) Recordings of 1203 tagged clicks of a single whale from the Bahamas with 120 sec of noise-only recording and

3) Recordings of over 15,000 manually tagged clicks from multiple whales we recorded on the Dominica Island together with 3.6 hours of noise-only data. \\ \\
The implementation code of our detector and our dataset for both SW clicks and noise transients, as well as our manual annotations are available in \cite{ceti}. \\ \\
Also see:
\begin{itemize}
    \item \href{https://www.projectceti.org/}{Project CETI}
    \item \href{https://www.projectceti.org/news-research-insights#publications}{Project CETI Publications}
    \item \href{https://www.youtube.com/playlist?list=PL-7Ju3RM0_oUKDIfBWlsOhONsXimWfMlF}{Project CETI Workshop - Decoding Communication in Nonhuman June 12-13, 2023 @ Simons Institute for the Theory of Computing}
\end{itemize}

>>>>

\section{Putting it all together}
The penalties are used for reinforcement learning applied to $M_{we}$. This process is repeated for all available paragraphs, potentially tens of thousands of times, effectively fine-tuning the model on a paragraph-by-paragraph basis.
Here is a summary of the training algorithm above:
\begin{algorithm}
\caption{Backtranslation Algorithm}
\begin{algorithmic}[1]
\STATE Initialize parameters $\theta$
\FOR{each iteration}
\STATE Translate whale vocalizations to English
\STATE Calculate probability penalty $Pwe$
\STATE Translate English back to whale
\STATE Calculate contextual and semantic penalties $Pwew$ and $Psd$
\STATE Update parameters $\theta$ based on combined penalties
\ENDFOR
\end{algorithmic}
\end{algorithm}
\subsection{Datasets}
The datasets provided a comprehensive set of whale vocalizations and environmental contexts, essential for training and evaluating our models.\\

I would primarily be interested in using two whale datasets for this work:

@@

2) Recordings of 1203 tagged clicks of a single whale from the Bahamas with 120 sec of noise-only recording and recordings of over 15,000 manually tagged clicks from multiple whales recorded on the Dominica Island together with 3.6 hours of noise-only data. \cite{ceti}. \\ \\
Also see:
\begin{itemize}
    \item \href{https://www.projectceti.org/}{Project CETI}
    \item \href{https://www.projectceti.org/news-research-insights#publications}{Project CETI Publications}
    \item \href{https://www.youtube.com/playlist?list=PL-7Ju3RM0_oUKDIfBWlsOhONsXimWfMlF}{Project CETI Workshop - Decoding Communication in Nonhuman June 12-13, 2023 @ Simons Institute for the Theory of Computing}
\end{itemize}
